Automatically Splitting a Two-Stage Lambda Calculus

### 2016-01-06 paper/paper.tex
format fiddling
changed paper style
various revisions
mostly formatting
formatting
quick edit pass based on reviews
cleaning and authors

\documentclass[preprint]{sigplanconf}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{mathpartir}
\usepackage{bbm}
\usepackage{mathabx}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{url}
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false,unicode=true]{hyperref}
\usepackage[usenames,dvipsnames]{color}
\usepackage{cprotect}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\PrerenderUnicode{λ}
\usepackage{verbatim}
\usepackage{xspace}

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem*{theorem*}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}

\input{macros}
\input{macros-ref}
\input{remarks}

\definecolor{stageOneColor}{RGB}{120,30,0}
\definecolor{stageTwoColor}{RGB}{0,0,127}
\definecolor{stageMonoColor}{RGB}{0,120,0}

@@

\lstset{%language=ML,
        columns=fullflexible,
        keepspaces=true,
        basicstyle=\ttfamily,
        tabsize=4,
%        escapeinside={"*}{*"},
        escapeinside={@}{@},
        moredelim=*[is][\color{stageOneColor}]{1`}{`},
        moredelim=*[is][\color{stageTwoColor}]{2`}{`},
        moredelim=*[is][\color{stageMonoColor}]{3`}{`},
        moredelim=*[is][\colorbox{black}]{4`}{`},
        literate={|->}{{\ $\mapsto$\ }}1
                 {xhat}{{$\hat{\texttt{x}}$}}1
                 {yhat}{{$\hat{\texttt{y}}$}}1
                 {zhat}{{$\hat{\texttt{z}}$}}1
                 {murec}{{$\mu$}}1
                 {alpha}{{$\alpha$}}1
                 {beta}{{$\beta$}}1
                 {atsign}{{@}}1
                 {literalone}{1}1 % hax
                 {literaltwo}{2}1 % hax
                 {^}{{$\curr$}}1
                 {$}{{$\fut$}}1}

@@

\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
\copyrightyear{20yy} 
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
%\doi{nnnnnnn.nnnnnnn}

% Uncomment one of the following two, if you are not going for the 
% traditional copyright transfer agreement.

@@

\title{Automatically Splitting a Two-Stage Lambda Calculus}
\subtitle{(Supplementary Material in Appendix)}

\authorinfo{~}%Nicolas Feltman \and Carlo Angiuli \and Umut A. Acar \and Kayvon Fatahalian}
           {~}%Carnegie Mellon University}
           {~}%\{nfeltman,cangiuli,umut,kayvonf\}@cs.cmu.edu}

@@

%\input{umut}

@@

\bibliography{paper}
\bibliographystyle{abbrvnat}

@@

\newpage\appendix
\input{appendix}

>>>>

\documentclass{llncs}

\usepackage{titlesec}  
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{proof}
\usepackage{mathpartir}
\usepackage{bbm}
\usepackage{mathabx}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{url}
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false,unicode=true]{hyperref}
\usepackage[usenames,dvipsnames]{color}
\usepackage{cprotect}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\PrerenderUnicode{λ}
\usepackage{verbatim}
\usepackage{xspace}

@@

%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{theorem*}{Theorem}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{remark}[theorem]{Remark}

\input{macros}
%\input{remarks}

\DeclareMathSymbol{\Gamma}{\mathalpha}{operators}{0}
\definecolor{stageOneColor}{RGB}{120,30,0}
\definecolor{stageTwoColor}{RGB}{0,30,127}
\definecolor{stageMonoColor}{RGB}{0,120,0}

@@

\lstset{%language=ML,
        columns=fullflexible,
        keepspaces=true,
        basicstyle=\ttfamily,
        tabsize=4,
%        escapeinside={"*}{*"},
        escapeinside={@}{@},
        moredelim=*[is][\color{stageOneColor}]{1`}{`},
        moredelim=*[is][\color{stageTwoColor}]{2`}{`},
        moredelim=*[is][\color{stageMonoColor}]{3`}{`},
        moredelim=*[is][\colorbox{black}]{4`}{`},
        literate={|->}{{\ $\mapsto$\ }}1
                 {xhat}{{$\hat{\texttt{x}}$}}1
                 {yhat}{{$\hat{\texttt{y}}$}}1
                 {zhat}{{$\hat{\texttt{z}}$}}1
                 {murec}{{$\mu$}}1
                 {alpha}{{$\alpha$}}1
                 {beta}{{$\beta$}}1
                 {atsign}{{@}}1
                 {literalone}{1}1 % hax
                 {literaltwo}{2}1 % hax
                 {^}{{$\curr$}}1
                 {$}{{$\fut$}}1}
\begin{comment}$\end{comment}
\lstset{aboveskip=3pt,belowskip=3pt}

@@

%\doi{nnnnnnn.nnnnnnn}

%
% Uncomment one of the following two, if you are not going for the 
% traditional copyright transfer agreement.

@@

\title{Automatically Splitting a Two-Stage Lambda Calculus}
%
\titlerunning{Automatic Splitting} 
%
\author{Nicolas Feltman\inst{1} \and Carlo Angiuli\inst{1}
\and Umut Acar\inst{1,2} \and Kayvon Fatahalian\inst{1}}
%
\authorrunning{Feltman et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Nicolas Feltman, Carlo Angiuli, Umut Acar, and Kayvon Fatahalian}
%
\institute{Carnegie Mellon University \and Inria Paris-Rocquencourt}

@@

@@

\newpage
\bibliography{paper}
\bibliographystyle{splncs03}

@@

%\newpage\appendix
%\input{appendix}
